Well-quasi-orderings on word languages

### 2025-10-14 src/prelims.tex
fix: mot and width of omega

\AP
Let $(X, \leq)$ be a \kl{well-quasi-ordered} set. One can define three
well-founded trees from $X$: the tree of \kl{bad sequences}, the tree of
decreasing sequences, and the tree of \kl{antichains}. The \kl{rank} of these
respective trees are called respectively the \intro{maximal order type} of $X$
written $\intro*{\oType{X}}$ \cite{dejongh77}, the \intro{ordinal height} of
$X$ written $\intro*{\oHeight{X}}$ \cite{schmidt81}, and the \intro{ordinal
width} of $X$ written $\intro*{\oWidth{X}}$ \cite{kriz90b}. These three
parameters are called the \intro{ordinal invariants} of a
\kl{well-quasi-ordered} set $X$. 
As an example, for $(\Nat, \leq)$, all bad sequences are descending and antichains have size at most $1$. Therefore the maximal order type and the ordinal height of $\Nat$ are $\omega$ and the ordinal width is $1$. \todo{Please check this!}
We refer to the survey of \cite{DZSCSC20} for
a detail discussion on these concepts and their computation on specific classes
of well-quasi-ordered sets.

>>>>

\AP Let $(X, \leq)$ be a \kl{well-quasi-ordered} set. One can define three
well-founded trees from $X$: the tree of \kl{bad sequences}, the tree of
decreasing sequences, and the tree of \kl{antichains}. The \kl{rank} of these
respective trees are called respectively the \intro{maximal order type} of $X$
written $\intro*{\oType{X}}$ \cite{dejongh77}, the \intro{ordinal height} of
$X$ written $\intro*{\oHeight{X}}$ \cite{schmidt81}, and the \intro{ordinal
width} of $X$ written $\intro*{\oWidth{X}}$ \cite{kriz90b}. These three
parameters are called the \intro{ordinal invariants} of a
\kl{well-quasi-ordered} set $X$. As an example, for $(\Nat, \leq)$, all bad
sequences are descending and antichains have size at most $1$. In fact, $(\Nat,
\leq)$ is itself an \kl{ordinal}, namely $\omegaOrd$. Hence it is its own
\kl{maximal order type} and \kl{ordinal height}, and its \kl{ordinal width} is
$1$ since it contains no antichain of size $2$. We refer to the survey of
\cite{DZSCSC20} for a detail discussion on these concepts and their computation
on specific classes of well-quasi-ordered sets.
